---
title: "CQL 2026 Challenge 3 - Monitoring Summary"
format:
  html:
    theme: flatly
    toc: true
    toc-location: left
    toc-depth: 3
    number-sections: true
date: today
date-format: "YYYY-MM-DD HH:mm"
execute:
  echo: false
  warning: false
  message: false
---

\*\*Last refreshed:\*\* \`r format(report_time, "%d %B %Y, %H:%M")\` NZ time

```{r}

#| label: load-libraries
#| include: false

library(tidyverse)
library(odbc)
library(DBI)
library(lubridate)
library(kableExtra)
library(knitr)
library(tables)
library(tibble)

# smaXtec API
library(httr)
library(rlist)
library(jsonlite)

knitr::opts_chunk$set(
  warning = FALSE,
  message = FALSE
)

# Explicit NZ date/time for automated rendering
report_time <- with_tz(Sys.time(), "Pacific/Auckland")
report_date <- as.Date(report_time)

```

```{r}

#| label: challenge-3-cows
#| include: false

challenge3_cows <- tribble(
  ~COWID, ~BIRTHID,       ~SMAXTEC_ID, ~CHALLENGE3,
  "4678", "LHMH-24-4678", "LHMH244678", "12hNoWater",
  "3668", "LHMH-23-3668", "LHMH233668", "12hNoWater",
  "2658", "LHMH-22-2658", "LHMH222658", "12hNoWater",
  "4183", "LHMH-24-4183", "LHMH244183", "12hNoWater",
  "3636", "LHMH-23-3636", "LHMH233636", "12hNoWater",
  "3612", "LHMH-23-3612", "LHMH233612", "12hNoWater",
  "4177", "LHMH-24-4177", "LHMH244177", "12hNoWater",
  "3675", "LHMH-23-3675", "LHMH233675", "12hNoWater",
  "601",  "JYTK-20-601",  "JYTK20601",  "12hNoWater",
  "625",  "JYTK-20-625",  "JYTK20625",  "12hNoWater",
  "2176", "LHMH-22-2176", "LHMH222176", "12hNoWater",
  "2670", "LHMH-22-2670", "LHMH222670", "12hNoWater",
  "4624", "LHMH-24-4624", "LHMH244624", "12hNoWater",
  "2178", "LHMH-22-2178", "LHMH222178", "12hNoWater",
  "2673", "LHMH-22-2673", "LHMH222673", "12hNoWater",
  "1634", "LHMH-21-1634", "LHMH211634", "12hNoWater",
  "665",  "JYTK-20-665",  "JYTK20665",  "12hNoWater",
  "671",  "JYTK-20-671",  "JYTK20671",  "12hNoWater",
  "677",  "JYTK-20-677",  "JYTK20677",  "12hNoWater",
  "4601", "LHMH-24-4601", "LHMH244601", "12hNoWater",
  "7673", "JYTK-17-7673", "JYTK177673", "12hNoWater",
  "7681", "JYTK-17-7681", "JYTK177681", "12hNoWater",

  "2638", "LHMH-22-2638", "LHMH222638", "Control",
  "3667", "LHMH-23-3667", "LHMH233667", "Control",
  "4676", "LHMH-24-4676", "LHMH244676", "Control",
  "4155", "LHMH-24-4155", "LHMH244155", "Control",
  "3679", "LHMH-23-3679", "LHMH233679", "Control",
  "2671", "LHMH-22-2671", "LHMH222671", "Control",
  "8155", "LHMH-18-8155", "LHMH188155", "Control",
  "3652", "LHMH-23-3652", "LHMH233652", "Control",
  "2646", "LHMH-22-2646", "LHMH222646", "Control",
  "3629", "LHMH-23-3629", "LHMH233629", "Control",
  "1682", "LHMH-21-1682", "LHMH211682", "Control",
  "1653", "LHMH-21-1653", "LHMH211653", "Control",
  "4156", "LHMH-24-4156", "LHMH244156", "Control",
  "4158", "LHMH-24-4158", "LHMH244158", "Control",
  "1687", "LHMH-21-1687", "LHMH211687", "Control",
  "9637", "JYTK-19-9637", "JYTK199637", "Control",
  "2629", "LHMH-22-2629", "LHMH222629", "Control",
  "9614", "JYTK-19-9614", "JYTK199614", "Control",
  "605",  "JYTK-20-605",  "JYTK20605",  "Control",
  "2159", "LHMH-22-2159", "LHMH222159", "Control",
  "636",  "JYTK-20-636",  "JYTK20636",  "Control",

  "3680", "LHMH-23-3680", "LHMH233680", "LowFlow",
  "3663", "LHMH-23-3663", "LHMH233663", "LowFlow",
  "2147", "LHMH-22-2147", "LHMH222147", "LowFlow",
  "4152", "LHMH-24-4152", "LHMH244152", "LowFlow",
  "3681", "LHMH-23-3681", "LHMH233681", "LowFlow",
  "4609", "LHMH-24-4609", "LHMH244609", "LowFlow",
  "2170", "LHMH-22-2170", "LHMH222170", "LowFlow",
  "3106", "LHMH-23-3106", "LHMH233106", "LowFlow",
  "691",  "JYTK-20-691",  "JYTK20691",  "LowFlow",
  "4172", "LHMH-24-4172", "LHMH244172", "LowFlow",
  "1606", "LHMH-21-1606", "LHMH211606", "LowFlow",
  "8265", "RRMN-18-8265", "RRMN188265", "LowFlow",
  "1661", "LHMH-21-1661", "LHMH211661", "LowFlow",
  "9688", "JYTK-19-9688", "JYTK199688", "LowFlow",
  "9648", "JYTK-19-9648", "JYTK199648", "LowFlow",
  "4610", "LHMH-24-4610", "LHMH244610", "LowFlow",
  "1642", "LHMH-21-1642", "LHMH211642", "LowFlow",
  "2114", "LHMH-22-2114", "LHMH222114", "LowFlow",
  "2645", "LHMH-22-2645", "LHMH222645", "LowFlow",
  "1639", "LHMH-21-1639", "LHMH211639", "LowFlow",
  "606",  "JYTK-20-606",  "JYTK20606",  "LowFlow",
  "3648", "LHMH-23-3648", "LHMH233648", "Control",
  "2137", "LHMH-22-2137", "LHMH222137", "LowFlow"
) %>% 
  mutate(COWID = as.numeric(COWID))

```

```{r}

#| label: api-smaxtec-connect
#| include: false

uid <- Sys.getenv("SMAXTEC_USER")
pw <- Sys.getenv("SMAXTEC_PASSWORD")

if (uid == "" || pw == "") {
  stop("smaXtec credentials are missing.")
}

resp <- POST("https://api.smaxtec.com/integration/v2/users/session_token?",
             query = list(user = uid, password = pw))

stop_for_status(resp)

token <- content(resp)$token


```

```{r}

#| label: api-smaxtec-load
#| include: false

to_date            <-"2026-12-12T00:00:00"
from_date          <-"2026-08-30T00:00:00"
aggregation_period <-"hourly"
timezone           <-"Pacific/Auckland"
timestamp_format   <-"iso"
metric <-"water_intake"

get_smaxtec_data<-function(animal_id, metric, token){
  
url<-paste0(
    "https://api.smaxtec.com/integration/v2/organisations/",
    "5fa1d66ea4a136b0b30df2b1",
    "/animals/",
    animal_id,
    "/data.json")

cat("URL:", url, "\n")
  
resp <- GET(url,
            query = list(
              to_date = to_date,
              aggregation_period = aggregation_period,
              from_date = from_date,
              timezone = timezone,
              timestamp_format = timestamp_format,
              metrics = metric
              ),
              add_headers(
              Accept="application/json", 
              Authorization=paste("Bearer", token)
              )
  )
  
stop_for_status(resp)
  
result<-content(resp,
          as = 'parsed',
          type = 'application/json') 

purrr::map_dfr(
  result[[1]]$data,
  ~tibble(
    timestamp = .x[[1]],
    value = .x[[2]]
  )
) %>% 
  
  mutate(animal_id = animal_id,
         metric = result[[1]]$metric,
         unit = result[[1]]$unit
         
         )
}

water_data <- purrr::map_dfr(
  challenge3_cows$SMAXTEC_ID,
  ~ get_smaxtec_data(
      animal_id = .x,
      metric = "water_intake",
      token = token
    )
)


```

```{r}

#| label: setup-script
#| include: false

knitr::opts_chunk$set(warning = FALSE, message = FALSE)

dairynz<-c("#00461e", "#ebb928", "#00d7ff", "#38A49A", "#fcfdfe", "#7FEBFF",  "#F5DC93", '#70f50a', 'black', '#3c9628', '#CDE9D9')

CalvingStart <-ymd_hms("2026-07-01 00:00:00")

water_data1<-water_data %>% 
  left_join(challenge3_cows, by = c('animal_id' = 'SMAXTEC_ID')) %>% 
  mutate(Date = as.Date(timestamp),
         DATE_TIME = ymd_hms(timestamp),
         hour = hour(DATE_TIME))

```

# Water Intakes

## Baseline Data - Herd Level - Water Intakes

First water intake was summarised for each cow daily and then summarised at the herd level

```{r}

#| label: challenge-monitor
#| echo: false

ncows<-water_data1 %>% 
  distinct(COWID, CHALLENGE3)

peakvalues<-water_data1 %>%
  filter(hour == 17) %>% 
  mutate(Week = isoweek(Date)) %>% 
  group_by(COWID, Week) %>% 
  mutate(WeekStartDate = min(Date)) %>% 
  ungroup() %>% 
  group_by(WeekStartDate, Date, hour) %>% 
  summarise(sum = sum(value)) %>% 
  group_by(WeekStartDate, hour) %>% 
  summarise(meanpeak = mean(sum)) %>% 
  select(c(WeekStartDate, meanpeak))

hourlyvalues<-water_data1 %>% 
  group_by(COWID, Date) %>% 
  summarise(n= n()) %>% 
  filter(n>=23)

smaxtecWaterIntake<-water_data1 %>% 
  semi_join(hourlyvalues) %>% 
  mutate(Week = isoweek(Date)) %>% 
  group_by(COWID, Week, CHALLENGE3) %>% 
  mutate(WeekStartDate = min(Date)) %>% 
  ungroup() %>% 
  group_by(COWID, WeekStartDate, Week, CHALLENGE3, Date) %>% 
  summarise(n = n(),
            sum = sum(value),
            min = min(value),
            max = max(value))

averagesbyweek<-smaxtecWaterIntake %>% 
  group_by(WeekStartDate) %>% 
  summarise(ndays = n_distinct(Date),
            mean = mean(sum),
            median = median(sum),
            sd = sd(sum),
            p10 = quantile(sum, 0.1),
            p90 = quantile(sum, 0.9),
            min = min(sum),
            max = max(sum),
            cv = (sd/mean)*100) %>% 
  left_join(peakvalues)


```

```{r}

#| label: herd-water
#| echo: false

kable(averagesbyweek, col.names = c('Week Start Date', 'N Days', 'Mean', 'Median', 'SD', 'P10', 'P90', 'Min', 'Max', 'CV', 'Peak'), 
      caption = '<b>Summary data for individual cow water intake (L/cow per d) for the Digital Welfare Indicators herd from the 1st September.<b>', align = c('l', rep('c', 10))) %>% 
  add_header_above(c(" " = 1, "Water intake (L/cow per d)" = 9, 'Herd intake' = 1), bold = TRUE) %>% 
  kable_classic(full_width = T, font_size = 16, html_font = 'Arial') %>% 
  row_spec(c(0), bold=T)

```

<br>

## Baseline Data - Challenge Group Level - Water Intakes

First water intake was summarised for each cow daily and then summarised at the challenge group level

```{r}

#| label: group-monitor
#| include: false

#Summarise at the group level by week

averagesbyweek_challenge<-smaxtecWaterIntake %>% 
  group_by(WeekStartDate, CHALLENGE3) %>% 
  summarise(mean = mean(sum),
            median = median(sum),
            sd = sd(sum),
            p10 = quantile(sum, 0.1),
            p90 = quantile(sum, 0.9),
            min = min(sum),
            max = max(sum),
            cv = (sd/mean)*100)

```

```{r}

#| label: group-monitor
#| echo: false

kable(averagesbyweek_challenge, col.names = c('Week Start Date', 'Challenge Grp', 'Mean', 'Median', 'SD', 'P10', 'P90', 'Min', 'Max', 'CV'), 
      caption = '<b>Summary data for individual cow water intake (L/cow per d) for the Digital Welfare Indicators herd from the 1st September.<b>', align = c(rep('l', 2), rep('c', 8))) %>% 
  add_header_above(c(" " = 2, "Water intake (L/cow per d)" = 8), bold = TRUE) %>% 
  kable_classic(full_width = T, font_size = 16, html_font = 'Arial') %>% 
  row_spec(c(0), bold=T)

```

<br>

```{r}

#| label: weekly-monitor-figure
#| echo: false
#| results: asis
#| fig.align: center
#| fig.cap: Weekly mean individual cow water intake at group level from Challenge 3
#| fig.height: 12
#| fig.width: 16

smaxtecWaterIntake %>% 
  group_by(WeekStartDate, CHALLENGE3) %>% 
  summarise(ndays = n_distinct(Date),
            mean = mean(sum),
            sd = sd(sum),
            sem = sd/sqrt(ndays)) %>% 
  filter(if (report_date >= as.Date('2026-11-02')) {
    WeekStartDate >= as.Date('2026-10-26') 
  } else {
    TRUE
  }
  ) %>% 
  ggplot(aes(x = WeekStartDate, y = mean, color = CHALLENGE3)) +
  geom_point(aes(color = CHALLENGE3), size = 3) +
  geom_errorbar(aes(ymin = mean - sem, ymax = mean + sem), width = 2) +
  scale_x_date(breaks = sort(unique(averagesbyweek_challenge$WeekStartDate)), date_labels = "%d-%b") +
  scale_y_continuous(breaks = seq(40, 100, by = 5)) +
  labs(y = 'Mean water intake, L/d', x = 'Week Start Date') +
  theme(legend.position = "top",
        #Axis text
        axis.text.x = element_text(angle = 45, size = 16, vjust = 1, hjust = 1),
        axis.text.y = element_text(size = 16),
        #Axis titles
        axis.title = element_text(size = 16),
        #Facets
        strip.text = element_text(size = 16, face = 'bold'),
        panel.spacing = unit(1, 'lines'),
        #Background
        panel.background = element_blank(),
        plot.background = element_blank(),
        #Remove y grid
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        #Borders
        panel.border = element_rect(color = 'black', fill = NA),
         #Legend
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        #Axis Lines
        axis.line.x = element_line(colour = "black", linewidth = 0.6),
        axis.line.y = element_line(colour = "black", linewidth = 0.6),
        axis.ticks = element_line(colour = "black", linewidth = 0.6))

```

<br>

# Monitoring Data - Individual Cow Water Intakes

<br>

If a cow’s daily water intake deviates from her own individual baseline median by more than two times her own baseline CV, expressed as an absolute percentage of her baseline median, she will be flagged for monitoring for another 24 h. If she does not return to her median baseline in 24 h, she will be removed from the 5-day exposure replicate.

```{r}

#| label: pre-baseline
#| echo: false

smaxtecWaterIntake1<-water_data1 %>% 
  semi_join(hourlyvalues) %>%
  mutate(TIMEPERIOD = case_when(Date >= as.Date("2026-11-06") & Date <=as.Date("2026-11-19") ~ 'Baseline',
                                Date >= as.Date("2026-11-20") ~ 'PostBaseline',
                                TRUE ~ 'PreBaseline')) %>% 
  group_by(TIMEPERIOD) %>% 
  mutate(PERIODSTARTDATE = min(Date)) %>%
  ungroup() %>% 
  group_by(COWID, Date, TIMEPERIOD, PERIODSTARTDATE) %>% 
  summarise(n = n(),
            sum = sum(value, na.rm=T),
            min = min(value, na.rm=T),
            max = max(value, na.rm=T))


averagebaseline<-smaxtecWaterIntake1 %>% 
  group_by(COWID, TIMEPERIOD, PERIODSTARTDATE) %>% 
  summarise(mean = mean(sum),
            median = median(sum),
            sd = sd(sum),
            cv = (sd/mean)*100) %>% 
  arrange(COWID) %>% 
  mutate(upper_limit = median + ((2*cv)/100 * median),
         lower_limit = median - ((2*cv)/100 * median)) %>% 
  filter(if (report_date >= as.Date("2026-11-20")) {
         TIMEPERIOD == 'Baseline'
          } else { TRUE })

dailychallenge<-water_data1 %>% 
  semi_join(hourlyvalues) %>%
  mutate(Date = as.Date(Date, format='%Y-%m-%d')) %>% 
  group_by(COWID, Date, CHALLENGE3) %>% 
  summarise(sum = sum(value, na.rm=T)) %>% 
  left_join(averagebaseline) %>% 
  mutate(flagged = sum < lower_limit | sum > upper_limit,
         high = sum > upper_limit,
         low = sum < lower_limit)
  
```

> **Prior to the 6th November**, the baseline is a pre-experimental baseline of all values between the 2026-08-31 to `r report_date`.

> **Inclusive of and after the 20th November**, the baseline is the actual baseline from the 2026-11-06 to 2026-11-19.

```{r}

#| label: daily-monitor
#| echo: false
#| results: asis
#| fig.align: center
#| fig.cap: Daily individual cow water intake from Challenge 3 start relative to their individual 2 week pre-treatment baseline for the previous 7 days
#| fig.height: 35
#| fig.width: 10

challenge_colours <- c(
  "Control" = "orange",
  "LowFlow" = "darkgreen",
  "12hNoWater" = "red"
)

challenge_plots<-dailychallenge %>% 
  ungroup() %>% 
  filter(Date >= report_date - 7 & Date <= report_date) %>% 
  arrange(CHALLENGE3, COWID, Date) %>% 
  group_split(CHALLENGE3) %>% 
  map(function(df) {
    
  challenge_name <- unique(df$CHALLENGE3)
  challenge_colour <- challenge_colours[as.character(challenge_name)]
  
  ggplot(df, aes(x = Date, y = sum)) +
  geom_line(linewidth = 1) +
  geom_point(aes(colour = flagged), size = 3) +
  geom_hline(aes(yintercept = median), linetype = 2) + 
  geom_hline(aes(yintercept = upper_limit), colour = "red") +
  geom_hline(aes(yintercept = lower_limit), colour = "red") +
  geom_text(data = df %>% filter(flagged == TRUE), aes(label = round(sum, 1)), vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold", show.legend = FALSE) +
  scale_x_date(breaks = sort(unique(dailychallenge$Date)), date_labels = "%d-%b") +
  facet_wrap(~ COWID, ncol = 2, scales = 'free_y') +
  labs(title = challenge_name,
      y = 'Water intake, L/d', x = 'Calendar Date', colour = 'Flagged') +
  theme(legend.position = "top",
        plot.title = element_text(size = 18, face = "bold", hjust = 0.5, colour = challenge_colour),
        axis.text.x = element_text(angle = 45, size = 14, vjust = 1, hjust = 1),
        axis.text.y = element_text(size = 14),
        axis.title = element_text(size = 16),
        strip.text = element_text(size = 14, face = 'bold', colour = 'white'),
        panel.spacing = unit(1, 'lines'),
        panel.background = element_blank(),
        plot.background = element_blank(),
        strip.background = element_rect(fill = challenge_colour, colour = 'black'),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_rect(color = 'black', fill = NA),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        axis.line.x = element_line(colour = "black", linewidth = 0.6),
        axis.line.y = element_line(colour = "black", linewidth = 0.6),
        axis.ticks = element_line(colour = "black", linewidth = 0.6))
  })

walk(challenge_plots, function(p) {
print(p)
cat("\n\n<br><br><br>\n\n")
})

```

## Today's Flagged Cows - Based on Water Intakes

```{r}

#| label: flagged-cows
#| echo: false

flag_cows <- function(data,
                         date = Date,
                         cow_id = COWID,
                         intake = sum,
                         high = high,
                         low = low,
                         trt = CHALLENGE3,
                         flagged = flagged) {
  
  result <- data %>%
    ungroup() %>%
    filter({{flagged}} == TRUE & {{date}} == report_date - 1) %>%
    select(
      {{ date }},
      {{ cow_id }},
      {{ trt }},
      {{ intake }},
      {{ high }},
      {{ low }},
      {{ flagged }}
    )
  
  if (nrow(result) == 0) {
    message(
      paste("No cows flagged on", report_date - 1)
    )
    
    return(invisible(NULL))
    
  } else {
    return(result)
  }
}

flagged_cows_water <- flag_cows(
  dailychallenge,
  date = Date,
  cow_id = COWID,
  trt = CHALLENGE3,
  intake = sum,
  high = high,
  low = low,
  flagged = flagged
)

if (!is.null(flagged_cows_water)) {
  
  kable(
    flagged_cows_water,
    col.names = c(
      "Date",
      "Cow ID",
      "Treatment",
      "Water intake, L/d",
      'High',
      'Low',
      'Flagged'
    ),
    caption = paste("**Cows flagged on", report_date - 1, "due to their water intake being +/- 2 CV from their mean baseline 2 weeks before trial start. High is TRUE indicates a higher than baseline value was flagged and Low is TRUE indicates a lower than baseline value was flagged.**"),
    align = c("l", "l", "l", 'l', 'l', "c", "c")
  ) %>%
    kable_classic(
      full_width = TRUE,
      font_size = 16,
      html_font = "Arial"
    ) %>%
    row_spec(0, bold = TRUE)
}

```

<br>

# Monitoring Milk Production

```{r}

#| label: setup-animalbase
#| include: false

SnowflakeCon1 <- DBI::dbConnect(odbc::odbc(),
                             Driver       = "SnowflakeDSIIDriver",
                             Server       = "dnz_economics.australia-east.azure.snowflakecomputing.com",
                             Authenticator = "Externalbrowser",
                             UID          = "STACEY.HENDRIKS@DAIRYNZ.CO.NZ",
                             PW = "",
                             Database     = "BRONZE",
                             Schema = 'CQL_DIGI_WOODY26',
                             Warehouse    = "COMPUTE_WH",
                             Tracing = 4, 
                             Role = 'ECONOMICS_READER',
)

TrialList    <- tbl(SnowflakeCon1, "VW_AB_TRIAL_ANIMAL")
AnimalList <-tbl(SnowflakeCon1, "VW_AB_ANIMAL") %>% 
  collect()

TrialGroupID <-tbl(SnowflakeCon1, "VW_AB_TRIAL_GROUP_ANIMAL") %>% 
  filter(TRIALGROUPID == 1439 | TRIALGROUPID == 1440) %>% 
  collect() %>% 
  select(c(ANIMALID, TRIALGROUPID))

TrialTrt<-tbl(SnowflakeCon1, "VW_AB_TRIAL_GROUP") %>% 
  collect() %>% 
  select(c(ID, NAME, TRIALID))

CowsEnrolled<-tbl(SnowflakeCon1, "ANIMAL_WOODY_RANDOMISATION") %>% 
  collect() %>% 
  right_join(challenge3_cows)

CowsEnrolled_sf<-copy_to(SnowflakeCon1, CowsEnrolled, temporary = TRUE, overwrite = TRUE)

AnimalBaseMilk <- tbl(SnowflakeCon1, "VW_AB_LACTATION_MILK_RESULT") %>%
  semi_join(CowsEnrolled_sf, by = "ANIMALID") %>% 
  left_join(CowsEnrolled_sf, by = "ANIMALID") %>%
  collect()

AnimalBaseMilk1<-AnimalBaseMilk %>% 
  filter(DATETIMERECORDED >= as.Date("2026-08-30")) %>%
  mutate(TIMEPERIOD = case_when(DATETIMERECORDED >= as.Date("2026-11-06") & DATETIMERECORDED <=as.Date("2026-11-19") ~ 'Baseline',
                                DATETIMERECORDED >= as.Date("2026-11-20") ~ 'PostBaseline',
                                TRUE ~ 'PreBaseline')) %>% 
  group_by(TIMEPERIOD) %>% 
  mutate(PERIODSTARTDATE = min(as.Date(DATETIMERECORDED))) %>%
  ungroup() %>% 
  select(-ID) %>% 
  left_join(TrialGroupID) %>% 
  left_join(TrialTrt, by = c('TRIALGROUPID' = 'ID')) %>% 
  mutate(DATETIMERECORDED = force_tz(DATETIMERECORDED, tzone = "Pacific/Auckland"),
         Date = as.Date(DATETIMERECORDED, tz = "Pacific/Auckland"),
         D_Time = hour(DATETIMERECORDED) + minute(DATETIMERECORDED) / 60,
         Session = ifelse(D_Time <= 9.5, "AM", "PM"),
         Date2 = if_else(Session == "PM", Date + 1, Date)) %>%
  relocate(D_Time, .after = DATETIMERECORDED) %>%
  relocate(Date, .after = DATETIMERECORDED) %>%
  relocate(Date2, .after = Date)

```

```{r}

#| label: daily-yields
#| echo: false

AnimalBaseMilk5 <- AnimalBaseMilk1 %>%
  mutate(PERIODSTARTDATE = min(Date)) %>% 
  filter(is.na(MILKWEIGHTKG) == FALSE) %>%
  group_by(COWID, CHALLENGE3, TIMEPERIOD, PERIODSTARTDATE, Date2) %>%
  summarise(MilkWt = sum(MILKWEIGHTKG, na.rm = TRUE), 
            n = n()) %>% 
  filter(n == 2) %>% 
  group_by(COWID, CHALLENGE3, TIMEPERIOD, PERIODSTARTDATE) %>%
  summarise(Avg_MilkWt = mean(MilkWt, na.rm = TRUE),
            SDMilkWt = sd(MilkWt, na.rm = TRUE),
            sem = SDMilkWt / sqrt(sum(!is.na(MilkWt)))) %>%   
  filter(if (report_date >= as.Date("2026-11-20")) {
         TIMEPERIOD == 'Baseline'
          } else { TRUE })

dailychallenge_milk<-AnimalBaseMilk1 %>%
  mutate(PERIODSTARTDATE = min(Date)) %>% 
  filter(is.na(MILKWEIGHTKG) == FALSE) %>%
  group_by(COWID, CHALLENGE3, TIMEPERIOD, PERIODSTARTDATE, Date2) %>%
  summarise(MilkWt = sum(MILKWEIGHTKG, na.rm = TRUE), 
            n = n()) %>% 
  filter(n == 2) %>% 
  select(-c(n)) %>% 
  left_join(AnimalBaseMilk5) %>% 
  mutate(upper_limit = (Avg_MilkWt*0.20) + Avg_MilkWt,
         lower_limit = Avg_MilkWt - (Avg_MilkWt*0.20),
         flagged = MilkWt < lower_limit | MilkWt > upper_limit,
         high = MilkWt > upper_limit,
         low = MilkWt < lower_limit)

```

<br>

> **Prior to the 6th November**, the baseline is a pre-experimental baseline of all values between the 2026-08-31 to `r Sys.Date()`.

> **Inclusive of the 20th November**, the baseline is the actual baseline from the 2026-11-06 to 2026-11-19.

```{r}

#| label: daily-monitor-milk
#| echo: false
#| results: asis
#| fig.align: center
#| fig.cap: Daily individual cow water milk yields from Challenge 3 start relative to their individual 2 week pre-treatment baseline for the previous 7 days
#| fig.height: 35
#| fig.width: 10

challenge_colours <- c(
  "Control" = "orange",
  "LowFlow" = "darkgreen",
  "12hNoWater" = "red"
)

challenge_plots_milk<-dailychallenge_milk %>% 
  ungroup() %>% 
  filter(Date2 >= report_date - 14 & Date2 <= report_date) %>% 
  arrange(CHALLENGE3, COWID, Date2) %>% 
  group_split(CHALLENGE3) %>% 
  map(function(df) {
    
  challenge_name <- unique(df$CHALLENGE3)
  challenge_colour <- challenge_colours[as.character(challenge_name)]
  
  ggplot(df, aes(x = Date2, y = MilkWt)) +
  geom_line(linewidth = 1) +
  geom_point(aes(colour = flagged), size = 3) +
  geom_hline(aes(yintercept = Avg_MilkWt), linetype = 2) + 
  geom_hline(aes(yintercept = upper_limit), colour = "red") +
  geom_hline(aes(yintercept = lower_limit), colour = "red") +
  geom_text(data = df %>% filter(flagged == TRUE), aes(label = round(MilkWt, 1)), vjust = 0.5, hjust = 1.5, size = 4, fontface = "bold", show.legend = FALSE) +
  scale_x_date(breaks = sort(unique(dailychallenge_milk$Date2)), date_labels = "%d-%b") +
  facet_wrap(~ COWID, ncol = 2, scales = 'free_y') +
  labs(title = challenge_name,
      y = 'Daily milk yield, L/d', x = 'Calendar Date', colour = 'Flagged') +
  theme(legend.position = "top",
        plot.title = element_text(size = 18, face = "bold", hjust = 0.5, colour = challenge_colour),
        axis.text.x = element_text(angle = 45, size = 14, vjust = 1, hjust = 1),
        axis.text.y = element_text(size = 14),
        axis.title = element_text(size = 16),
        strip.text = element_text(size = 14, face = 'bold', colour = 'white'),
        panel.spacing = unit(1, 'lines'),
        panel.background = element_blank(),
        plot.background = element_blank(),
        strip.background = element_rect(fill = challenge_colour, colour = 'black'),
        panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(),
        panel.border = element_rect(color = 'black', fill = NA),
        legend.text = element_text(size = 16),
        legend.title = element_text(size = 16),
        axis.line.x = element_line(colour = "black", linewidth = 0.6),
        axis.line.y = element_line(colour = "black", linewidth = 0.6),
        axis.ticks = element_line(colour = "black", linewidth = 0.6))
  })

walk(challenge_plots_milk, function(p) {
print(p)
cat("\n\n<br><br><br>\n\n")
})

```

## This week's Flagged Cows - Based on Daily Milk Yield

<br>

> There is a \~5 day lag in data coming from the milk meters into Snowflake, and therefore, the flagged cows represent those flagged in the previous \~10 days but may not include more recent data.

```{r}

#| label: flagged-cow-milk
#| echo: false


flag_cows_milk <- function(data,
                         date = Date2,
                         cow_id = COWID,
                         milkyield = MilkWt,
                         high = high,
                         low = low,
                         trt = CHALLENGE3,
                         flagged = flagged) {
  
  result <- data %>%
    ungroup() %>%
    filter({{flagged}} == TRUE & {{date}} >= report_date - 10,
           {{date}} <= report_date) %>%
    select(
      {{ date }},
      {{ cow_id }},
      {{ trt }},
      {{ milkyield }},
      {{ high }},
      {{ low }},
      {{ flagged }}
    ) %>% 
    arrange({{ cow_id }}, {{ date }})
  
  if (nrow(result) == 0) {
    message(
      paste("No cows flagged on", report_date - 1)
    )
    
    return(invisible(NULL))
    
  } else {
    return(result)
  }
}

flagged_cows_milk <- flag_cows_milk(
  dailychallenge_milk,
  date = Date2,
  cow_id = COWID,
  trt = CHALLENGE3,
  milkyield = MilkWt,
  high = high,
  low = low,
  flagged = flagged
)

if (!is.null(flagged_cows_milk)) {
  
  kable(
    flagged_cows_milk,
    col.names = c(
      "Date",
      "Cow ID",
      "Treatment",
      "Milk yield, L/d",
      'High',
      'Low',
      'Flagged'
    ),
    caption = "<b>Cows flagged in the previous 10 days due to their milk yield being +/- 20% from their mean baseline 2 weeks before trial start. High is TRUE indicates a higher than baseline value was flagged and Low is TRUE indicates a lower than baseline value was flagged.<b>",
    align = c("l", "l", "l", 'l', 'l', "c", "c")
  ) %>%
    kable_classic(
      full_width = TRUE,
      font_size = 16,
      html_font = "Arial"
    ) %>%
    row_spec(0, bold = TRUE)
}

```
